---
title: "avrc_bools WIP v1"
author: "Andrew Frick"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{str_comb_X Functions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
library(tidyverse)
library(AVRCHelp)
knitr::opts_chunk$set(echo = TRUE)
```

One of the first "oops" mistakes I had in R had to do with T | NA == NA instead
of false. While there are times when you don't want to coerce that to false, I
decided to create a new set of boolean operators for this case.

First we'll look at the new `equal to` operator `%==%` by creating a data frame of 
boolean combinations

```{r}
#Create data frame/tibble with combination of all bools

x = c(T,F,NA)

bools = as.tibble(expand.grid(x,x))

equals = bools %>% 
  mutate(`==` = (Var1 == Var2),
         `%==%` = (Var1 %==% Var2))
```

Below you can see the difference in the output for the original `==` and the 
`%==%` extension.

```{r}
equals
```

Here we'll create another tibble containing the 'venn diagram' boolean operators

1. `|` vs `%or%`
2. `&` vs `%&%`

```{r}

Venns = bools %>% 
  mutate(`|` = (Var1 | Var2),
         `%or%` = (Var1 %or% Var2),
         `&` = (Var1 & Var2),
         `%&%` = (Var1 %&% Var2))

```


```{r}
Venns
```

The equality operator also allows comparison of a single value vs a vector, it
can be used for subsetting operations. 

```{r}

y = 'blue'

colors = c('blue', 'red', 'yellow', NA)

colorsamp = sample(colors, size = 10, prob = c(0.2,0.2,0.3,0.3),
                   replace = T)


y  ==  colorsamp
y %==% colorsamp

```

